Calculating life expectancy and exploring missingness

### 2016-10-26 Code/1_Explore_Data_v2.Rmd

first <- first %>% 
  arrange(Ages, sign, Cause.of.death) %>%
  group_by(group) %>%
  mutate(lag = lag(C_xi), one = 1, 
         num = cumsum(one),
         length = n(),
         start = ifelse(is.na(lag)==T, 0, NA),
         finish = ifelse(is.na(lag)==T, C_xi, NA))
View(first)

@@

  updated <- rbind(updated, subset)
}
updated 
```

>>>>

first <- first %>% 
  arrange(Ages, sign, Cause.of.death) %>%
  group_by(group) %>%
  mutate(lag = lag(C_xi), one = 1, 
         num = cumsum(one),
         start = ifelse(is.na(lag)==T, 0, NA),
         finish = ifelse(is.na(lag)==T, C_xi, NA))
View(first)

@@

  updated <- rbind(updated, subset)
}
View(updated)

ggplotly(ggplot(updated, aes(y = Ages, x = start)) + 
           geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
           xlab("Contribution to life expectancy gap") +
           ylab("Age group\n") + theme_minimal() +
           geom_vline(xintercept = 0))
```
